% !TEX root = ../utltcp-paper.tex

In this paper we described the rationale for the use new transport services
for real-time application in the Internet, then presented TCP Hollywood, a 
modified TCP that is designed to address these needs.
Our analysis shows that our suggested modifications to TCP are beneficial
to applications with tight latency bounds, such as voice telephony. This
is validated through performance evaluation under network emulation. The
appendix to this paper discusses reproducibility of these results.
We have further shown that by limiting the wire-visible modifications, 
TCP Hollywood can maintain TCP's widespread ease of deployment.

Future work will include performance evaluation on the public Internet, to 
show that the gains we show through analysis and simulation are achievable
in practice. 
Beyond this, we are exploring enhancements to TCP Hollywood that may
further improve performance. For example, dependency information is
currently used to determine when \textit{not} to send a message, but it may
be a cause \textit{to} send a message, even if that message may not arrive
in time to be played out, to allow future messages to be processed. Broader
enhancements, such as integration with SACK or MP-TCP, should also be
studied.

TCP Hollywood exists within a transport-layer protocol design space that
is constrained by ossification. We have TCP and UDP as substrates, with
little room for modification. Substrate selection presents trade-offs:
TCP gives a wider deployment story than UDP, but depending on the desired
functionality, receiver-side kernel modifications can be needed.
These trade-offs may shift over time, as the network responds to large
deployments of substrate-based transports. For example, QUIC is seeing
non-trivial deployment by being included within Google's web browser, and
may result in fewer firewalls blocking UDP. This is a long-term concern,
however, and in the near future we believe that protocols like TCP
Hollywood offer important advantages relating to middlebox traversal,
that will make them easy and valuable to deploy. Our initial results
show TCP Hollywood is deployable on \emph{all} major fixed and mobile
operators in the UK, offering compelling latency advantages.

